Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-03-09 manuscript/climate_sensitivity_SI.Rmd
misc cleanup

\newpage
```{r, Table S3, eval=TRUE, echo=FALSE, message=FALSE}
tableS3 <- read.csv("tables_figures/drought_stats.csv", stringsAsFactors = FALSE)
kable(tableS3, booktabs=TRUE, format = "latex", caption = "Table S3: Palmer drought severity index (PDSI) by month for years with widespread growth reduction") %>%
  pack_rows("focal droughts", 1, 4, latex_gap_space = ".4em", colnum = 3, hline_before = FALSE) %>%
  pack_rows("", 5, 8, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 9, 12, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("other", 13, 16, latex_gap_space = ".4em", colnum = 3, hline_before = FALSE) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

>>>>

\newpage
```{r, Table S3, eval=TRUE, echo=FALSE, message=FALSE}
tableS3 <- read.csv("tables_figures/drought_stats.csv", stringsAsFactors = FALSE)
kable(tableS3, booktabs=TRUE, format = "latex", caption = "Table S3: Palmer drought severity index (PDSI) by month for focal droughts") %>%
  pack_rows("focal droughts", 1, 4, latex_gap_space = ".4em", colnum = 3, hline_before = FALSE) %>%
  pack_rows("", 5, 8, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 9, 12, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("other", 13, 16, latex_gap_space = ".4em", colnum = 3, hline_before = FALSE) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

### 2020-03-09 manuscript/climate_sensitivity_draft.Rmd
misc cleanup

**Title:** Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest (**[issue #84](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/84))

@@

- We conclude that hydraulic traits and tree height influence growth responses during drought, and can explain variation in the tree-ring record spanning historical droughts. Thus, these factors can be useful for predicting future drought responses under climate change. (**LS suggests take out "influence growth responses during drought, and". I agree this conclusion is a bit repetitive/could be shortened, but would target the "explain variation..." for removal** - *I agree with this*)

@@

All analysis beyond basic data collection was performed using R version 3.5.3 [@R-base]. All data, code, and results are available through the SCBI-ForestGEO organization on GitHub (https://github.com/SCBI-ForestGEO: SCBI-ForestGEO-Data and McGregor_climate-sensitivity-variation repositories), with static versions corresponding to data and analyses presented here archived in Zenodo (DOIs: 10.5281/zenodo.3604993 and [TBD], respectively **krista just to remind you this TBD is here**).

@@

Table S3: Palmer drought severity index (PDSI) by month for years with widespread growth reduction

>>>>

**Title:** Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

@@

- We conclude that hydraulic traits and tree height influence growth responses during drought, as recorded in the tree-ring record spanning historical droughts. Thus, these factors can be useful for predicting future drought responses under climate change.

@@

All analysis beyond basic data collection was performed using R version 3.5.3 [@R-base]. All data, code, and results are available through the SCBI-ForestGEO organization on GitHub (https://github.com/SCBI-ForestGEO: SCBI-ForestGEO-Data and McGregor_climate-sensitivity-variation repositories), with static versions corresponding to data and analyses presented here archived in Zenodo (DOIs: 10.5281/zenodo.3604993 and [TBD], respectively.

@@

Table S3: Palmer drought severity index (PDSI) by month for focal droughts
